Scalable Clustering of Genotype Information using MapReduce

### 2014-05-16 doc/publications/incob2014/paper.tex
Signed-off-by: Aidan O'Brien <ayduno@gmail.com>

\section*{Results and discussion}
\subsection*{Runtime}
We measured the runtime seperately for pre-processing stage as well as the k-means clustering stage.

@@

@@

>>>>

\section*{Results and discussion}
\subsection*{Runtime}
We measured the runtime seperately for pre-processing stage as well as the k-means clustering stage. 
Pre-processing the data to Mahout's sequence files took approximately 21 minutes (1255s) and used approximately 1.8GB (1831160kb) physical memory (pmem) and 7.6GB (7646232kb) virtual memory (vmem). Conversly,  pre-processing
the data to R's in memory matrix took approximately 56 minutes (3341s) and used approximately 17.7GB (17696940kb) pmem and 18GB (18000196kb) vmem.

@@

\subsection*{Hardware}
We processed the data using a Portable Batch System (PBS) cluster. We allocated one node and 64GB memory for the comparison between Mahout and R.
Each node has eight CPU cores, however both applications run a single thread for pre-processing the data.
For the (\FullPop) dataset, we ran the job on a PBS cluster of x nodes, with twelve CPU cores and 48GB of memory per node.

@@

\subsection*{R K-means clustering}
We use 'readVcf' from the R library, 'VariantAnnotation', to iteratively read in the VCF file. For each iteration, we convert the data to a matrix and
change the values for each variant to the Hamming distance, as mentioned previously. We then transpose the matrix, so individuals are represented
by rows, and append the matrix to that from the previous iteration. Once the matrix contains all of the variants from the VCF file, we cluster the data
using the 'kmeans' algorithm from the 'stats' library.
